Modeling costs and benefits of genomic wastewater surveillance

### 2023-05-12 paper/model-documentation.qmd
updating model documentation, trying out stochastic implementation with odin

This paper develops a stochastic metapopulation disease transmission model and uses it to assess the conditions under which WBS systems can provide value to local public health decision makers who respond to a pandemic using surveillance data. We evaluate a range of scenarios that represent different potential pathogens and highlight scenarios under which WBS systems may or may not be cost-effective.
<!--
Our results highlight that the value of WBS systems is contingent on a set of biological and societal parameters, including pathogen characteristics (i.e., transmissibility and severity), as well as the geographic scale of 
-->
# Methods

>>>>

This paper develops a stochastic metapopulation disease transmission model and uses it to assess the conditions under which WBS systems can provide value to local public health decision makers who respond to a pandemic using surveillance data. We evaluate a range of scenarios that represent different potential pathogens and highlight scenarios under which WBS systems may or may not be cost-effective.
<!--
Our results highlight that the value of WBS systems is contingent on a set of biological and societal parameters, including pathogen characteristics (i.e., transmissibility and severity), as well as the geographic scale of 
-->

# Methods
